### 2022-02-13 prior_versions/arxiv/experiments.tex
update

\begin{figure*}[!t]
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/same_covariates.eps}
		\caption{Example \ref{ex_same_cov}}
		\label{fig_same_cov}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d.eps}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/covariate_shift.eps}
		\caption{Example \ref{ex_covshift}}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%Three takeaways of our theory in Section \ref{sec_insight}.
	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomenon by fixing task two's sample size and increasing task one's sample size.
	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
%	Depending on how large the distance $d^2$ is, task two's prediction loss decreases initially before increasing again, or decreases monotonically.
	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
	Having covariate shifts increases task two's prediction loss when task two's sample size is smaller than task one. Otherwise, having covariate shifts (surprisingly) decreases task two's prediction loss.}
	\label{fig_model_shift_phasetrans}
\end{figure*}

\paragraph{Sample efficiency.}
First, we validate the result of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss over ten tasks as we increase the number of samples per-task from $400$ to $2000$.
In all the parameter settings, our results estimate the empirical losses accurately.
We also observe a trend that the average prediction loss increases as we increase distance $d$ from $0.1$ to $0.2$.
Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
%Second, when $d = 0.1$, we have that $d^2 \le \frac{\sigma^2 p}{n - p}$ for all values of $n$, hence the average prediction loss of hard parameter sharing is always lower than STL.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level. %\FY{I do not quite understand this sentence about "3x fewer", because how much data needed depends on $d$ and the prediction loss level we are looking at. For example, at the cross point, this ratio is 1. }

\paragraph{Sample size ratio.}
Second, we validate the result of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
%Again, our estimates are accurate compared to the empirical losses.
We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$. We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
Intuitively, this is because bias increases less for smaller $d^2$.
%Our result from Corollary \ref{cor_MTL_loss} explains this trend.

\paragraph{Covariate shift.}
Finally, we validate the result of Example \ref{ex_covshift}.
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
%Covariate shift: We set $\kappa = 1$ and $d = 0$.
%We set $\rho_2 = 4$ and vary $\rho_1$ from $5$ to $25$ for sample sizes.
%We use the scale parameter $\lambda = 1$ for the curve without covariate shift and $\lambda = 2$ for the curve with covariate shift (cf. Section \ref{sec_covshift}).

%Recall that Section \ref{sec_data_size} shows that increasing the data size of the source task does not always improve the performance of MTL for the target task.
%In Figure \ref{fig_ab_data}, we show that for source task MR and target task SST, there is a transition from positive to negative transfer as we increase the data size of the source task.
%Our result provides a fine-grained insight on the covariance alignment algorithm proposed in \cite{WZR20}.
%Recall that the covariance alignment procedure in \cite{WZR20} adds an additional module between the word embedding representation and the shared module.
%When the source task data size is particularly large compared to the target task, we show that applying the covariance alignment algorithm results in more significant gains.
%In Figure \ref{fig_ab_cov}, we observe that the benefit from aligning task covariances becomes more significant for LSTM and MLP as we increase the number of datapoints of the source task.

%\begin{table}
%	\begin{center}
%		\begin{tabular}{c c c c c}
%			\toprule
%			\multirow{2}{*}{{\bf Models}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}
%				                                                                          MR, SST, SUBJ, CR, MPQA, TREC\end{center}\end{minipage}} & \multicolumn{2}{c}{\begin{minipage}{1.1in}\begin{center}MR, SST, SUBJ, CR, MPQA\end{center}\end{minipage}} \\
%			\cmidrule(lr){2-3} \cmidrule(lr){4-5}
%			& {\bf Stanford} & {\bf Alignment} & {\bf Stanford} & {\bf Alignment} \\
%			\midrule
%			{\bf MLP}  & > 100\% & 39\% & 25\% & 25\% \\
%			{\bf LSTM} & 36\% & 36\% & 28\% & 25\% \\
			% {\bf CNN}  & 76\% & - & 32\% & -\\
%			\bottomrule
%		\end{tabular}
%	\end{center}
%	\caption{Taskonomy experiment.}
%	\label{tab:taskonomy}
%\end{table}
%\begin{figure}[!t]
%	\centering
%	\includegraphics[width=0.35\textwidth]{figures/same_covariates.eps}
%	\caption{Validating Example \ref{ex_same_cov} in Section \ref{sec_same} for $10$ tasks: our estimated loss (solid line) matches the empirical loss (dotted line) accurately for various task-specific variance $d^2$ and sample size $n$ settings. The feature dimension $p$ is $200$, and noise variance $\sigma^2$ is $1/4$.}
%	\label{fig_same_cov}
%\end{figure}

>>>>

\begin{figure*}[!t]
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/same_covariates-eps-converted-to.pdf}
		\caption{Example \ref{ex_same_cov}}
		\label{fig_same_cov}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/sample_ratio_several_d-eps-converted-to.pdf}
		\caption{Example \ref{ex_sample_ratio}}
		\label{fig_size}
	\end{subfigure}\hfill
	\begin{subfigure}[b]{0.33\textwidth}
		\centering
		\includegraphics[width=0.98\textwidth]{figures/covariate_shift-eps-converted-to.pdf}
		\caption{Example \ref{ex_covshift}}
		\label{fig_covariate}
	\end{subfigure}
	\caption{%
	Our estimated losses (solid line) match the empirical losses (dotted line) accurately under various settings in dimension $p = 200$.
	\textbf{Left.} Validating Example \ref{ex_same_cov} for ten tasks: the noise variance $\sigma^2$ is $1/4$.
	\textbf{Middle.} Validating Example \ref{ex_sample_ratio} for two tasks: we discover an interesting phenomenon by fixing task two's sample size and increasing task one's sample size.
	Moreover, our result accurately predicts the critical point (marked in circle) of the loss curve.
	\textbf{Right.} We show how different levels of covariate shift affect hard parameter sharing when there is no bias.
	Having covariate shifts increases task two's prediction loss when task two's sample size is smaller than task one. Otherwise, having covariate shifts (surprisingly) decreases task two's prediction loss.}
	\label{fig_model_shift_phasetrans}
\end{figure*}

\paragraph{Sample efficiency.}
First, we validate the result of Example \ref{ex_same_cov}.
Figure \ref{fig_same_cov} shows the average prediction loss over ten tasks as we increase the number of samples per-task from $400$ to $2000$.
In all the parameter settings, our results estimate the empirical losses accurately.
We also observe a trend that the average prediction loss increases as we increase distance $d$ from $0.1$ to $0.2$.
Our work explains the differences between these two settings since $d^2 = 0.1^2$ is always smaller than $\frac{\sigma^2 p}{n - p}$, but $d^2 = 0.2^2$ is not.
Indeed, we observe a crossover point between hard parameter sharing and STL.
Finally, for $d = 0.2$, looking horizontally, we find that HPS requires fewer samples per-task than STL to achieve the same loss level. %

\paragraph{Sample size ratio.}
Second, we validate the result of Example \ref{ex_sample_ratio}.
Figure \ref{fig_size} shows task two's prediction loss  as we increase the sample ratio $n_1 / n_2$ from $1/10$ to $7/10$.
We consider a regime where task two consists of $80,000$ samples, and task one's sample size varies from $8,000$ to $56,000$. 
The task-specific variance (which scales with model distance) is $d = 0.2$, the noise variance is $\sigma^2 = 4^2$, and the shared signal variance is $1$. We observe that as we increase the sample ratio, task two's prediction loss decreases initially but later will increase when the sample ratio is above a certain level.
On the other hand, when $d = 0.15$, task two's prediction loss decreases faster.
Intuitively, this is because bias increases less for smaller $d^2$.

\paragraph{Covariate shift.}
Finally, we validate the result of Example \ref{ex_covshift}.
Figure \ref{fig_covariate} shows task two's prediction loss as we increase task one's sample size.
Recall that $\lambda$ measures the severity of covariate shifts---a larger $\lambda$ means a larger covariate shift.
We indeed observe the dichotomy in Example \ref{ex_covshift} at $n_1 = 800$.
The sample size $n_2$ is $800$ and the noise variance $\sigma^2$ is $1/4$.
